To Be Decided

### 2025-07-18 paper/main.tex
Beginning of the section IV-B

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.pdf}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.pdf}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.pdf}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.pdf}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.pdf}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.pdf}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.pdf}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.pdf}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.pdf}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.pdf}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.pdf}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.pdf}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

                \begin{figure}
                    \centering
                    \includegraphics[width=.9\columnwidth]{../experiments/average/figs/confidence_intervals.pdf}
                    \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
                    \label{fig:shape:average:confidence_intervals}
                \end{figure}

@@

>>>>

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.eps}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.eps}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.eps}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.eps}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.eps}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.eps}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.eps}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.eps}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.eps}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.eps}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

                \begin{figure}
                    \centering
                    \includegraphics[width=.8\columnwidth]{../experiments/average/figs/confidence_intervals.pdf}
                    \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
                    \label{fig:shape:average:confidence_intervals}
                \end{figure}

@@

            % Em muitas configurações nas quais os algoritmos conseguem reconstruir adequadamene a geometria dos espalhadores, o erro na detecção da posição dos espalhadores tende a ser baixo. Por exemplo, no estudo da seção \ref{sec:results:shape:star}, o indicador $\zeta_P$ obtido pelo LSM, OSM, BIM, CSI e SOM foram, respectivamente, 0.049\%, 0.057\%, 0.25\%, 0.31\% e 0.14\%. Isto porque a geometria e a posição são características dos espalhadores que, normalmente, os algoritmos não lidam com isso em separado.

            In many scenarios where algorithms can adequately reconstruct the geometry of scatterers, the error in detecting scatterer positions tends to be low. For example, in the study described in Section \ref{sec:results:shape:star}, the $\zeta_P$ indicator values obtained by LSM, OSM, BIM, CSI, and SOM were 0.049\%, 0.057\%, 0.25\%, 0.31\%, and 0.14\%, respectively. This occurs because geometry and position are scatterer characteristics that algorithms typically do not handle separately.

            % Uma exceção seria no caso de algoritmos que resolvem o problema de imageamento como um problema de otimização no qual as variáveis de decisão são a posição, os vértices (ou outras características de uma geometria predefinida) e o contraste dos espalhadores \cite{michalski2000electromagnetic,salucci2022learned,zardi2025physics}. Além disso, em cenários com espalhadores fortes, os métodos tradicionais geralmente não conseguem recuperar muito bem a geometria dos espalhadores, dada a maior dificuldade do problema. Nesses cenários, o estudo da detecção da posição pode ser mais relevante.

            An exception would be algorithms that solve the imaging problem as an optimization problem, where the decision variables are the position, vertices (or other characteristics of a predefined geometry), and contrast of the scatterers \cite{michalski2000electromagnetic,salucci2022learned,zardi2025physics}. Additionally, in scenarios involving strong scatterers, traditional methods generally struggle to recover scatterer geometry effectively due to the increased problem hardness. In such scenarios, studying position detection becomes more relevant.

            % Levando isso em consideração, os experimentos dessa seção foram formulados considerando espalhadores fortes, nos quais os métodos tradicionais não conseguem recuperar adequadamente a geometria dos espalhadores. Com isso, o indicador de erro de posição $\zeta_P$ pode ser uma métrica relevante para comparar desempenho nesse tipo de cenário.

            Considering this, the experiments in this section were designed for scenarios involving strong scatterers, where traditional methods cannot adequately recover scatterer geometry. Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.
